\begin{longtab}
%\begin{landscape}
\begin{longtable}{c c c c c c}
\caption{Balmer lines fluxes of GRB hosts\label{tab:balmerlines}}\\
\hline\hline
{GRB host} & {Redshift} & $\rm{H}\delta$ & $\rm{H}\gamma$ & $\rm{H}\beta$ & $\rm{H}\alpha$ \\
\hline
\endfirsthead
\hline
\caption{Balmer lines fluxes (continued)}\\
\hline\hline
{GRB host} & {Redshift} & $\rm{H}\delta$ & $\rm{H}\gamma$ & $\rm{H}\beta$ & $\rm{H}\alpha$ \\
\hline
\endhead
\input{tables/Xshooter_balmer_fluxes.tex}
\hline\noalign{\smallskip}
\end{longtable}
\centering
\begin{minipage}{5.8in}
\tablefoot{
Measurements are in units of $10^{-17}$\,\erg, and are corrected for the Galactic foreground reddening. A correction for slit-loss based on broad-band photometry has been applied to the measurements as described in the text. These values thus represent host-integrated measurements except for GRB~100316D (see below). Line fluxes are not corrected for host-intrinsic extinction. The first error represents the statistical error due to photon statistics and line-flux measurement. The second error is the systematic error in the absolute flux calibration due to slit-loss and scaling to photometry. Redshifts are given in a heliocentric reference frame. No data means that either the wavelength range of the respective lines is not covered, all data in that wavelength range have been excluded from the automated fitting procedure, or no meaningful constraints could be obtained for the given line.\\
$^{a}$ With the lowest redshift in the sample of $z=0.0592$, GRB~100316D is very close-by. The fraction of the host that is covered by the slit is thus so small that it does not allow us to derive host-integrated measurements. These values are thus as derived from the observed spectrum and not scaled by photometry. No systematic error on the line fluxes is given in this case.}
\end{minipage}

%\end{landscape}
\end{longtab}
